Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-01 paper.tex
Address reviewer 2 comments on page 2

In the pursuit of a fully sustainable energy profile, cross-flow (often
vertical-axis) turbines (CFTs) can still play a role. Despite extensive research
and development in the 1970s through the early 1990s by groups like Sandia
National Labs in the US \cite{Sutherland2012} and the National Research Council
in Canada \cite{Para2002}, the vertical-axis cross-flow Darrieus turbines were
all but abandoned for large scale commercial terrestrial wind power. Today,
however, with the development of marine hydrokinetic (MHK) energy devices, CFTs
are at the forefront, with the first grid-connected commercial device being a
horizontal-axis CFT manufactured and installed by ORPC in Cobscook Bay, Maine
\cite{ORPC2012}. CFTs are also being examined for small-scale onshore wind in
urban areas \cite{Lott2015}, offshore floating wind farms \cite{Paulsen2011,
Sandia2012}, and onshore wind farms where power output per unit land area is of
interest \cite{Dabiri2011}.

Despite the development of many simple engineering models based on blade element
momentum or vortex methods, it remains difficult to predict the performance of
cross-flow turbines for all cases---namely when solidity, or blade
chord-to-radius ratio is high---a common characteristic of smaller rotors, and
those designed for marine hydrokinetic (MHK) applications. With computing power
becoming evermore available and affordable, CFD based on the Reynolds-averaged
Navier--Stokes (RANS) equations has become an attractive method for predicting
the performance of cross-flow turbines. Since a direct numerical simulation
(DNS) of all scales at realistic Reynolds numbers is not currently feasible,
turbulence be modeled. However, with an appropriate turbulence model,
blade-resolved RANS presents a more physically realistic first principles based
approach versus simpler models based on momentum theory or potential flow.
However, CFD can be computationally expensive when done in three dimensions,
which may be necessary in some cases.

>>>>

In the pursuit of a fully sustainable energy profile, cross-flow (often
vertical-axis) turbines (CFTs) can still play a role. Despite extensive research
and development in the 1970s through the early 1990s by groups like Sandia
National Labs in the US \cite{Sutherland2012} and the National Research Council
in Canada \cite{Para2002}, vertical-axis cross-flow Darrieus turbines were all
but abandoned for large scale commercial terrestrial wind power. Today however,
with the development of marine hydrokinetic (MHK) energy devices, CFTs are at
the forefront, with the first grid-connected commercial device being a
horizontal-axis CFT manufactured and installed by ORPC in Cobscook Bay, Maine
\cite{ORPC2012}. CFTs are also being examined for small-scale onshore wind in
urban areas \cite{Lott2015}, offshore floating wind farms \cite{Paulsen2011,
Sandia2012}, and onshore wind farms where power output per unit land area is of
interest \cite{Dabiri2011}.

Despite the development of many simple engineering models based on blade element
momentum or vortex methods, it remains difficult to predict the performance of
cross-flow turbines when solidity, or blade chord-to-radius ratio is high---a
common characteristic of smaller rotors, and those designed for marine
hydrokinetic (MHK) applications, since water's higher density increases rotor
loading by roughly an order of magnitude for the same frontal
area~\cite{Bachant2016-thesis}. With computing power becoming evermore available
and affordable, CFD based on the Reynolds-averaged Navier--Stokes (RANS)
equations has become an attractive method for predicting the performance of
cross-flow turbines. Since a direct numerical simulation (DNS) of all scales at
realistic Reynolds numbers is not currently feasible, turbulence be modeled.
However, with an appropriate turbulence model, blade-resolved RANS presents a
more physically realistic first principles based approach versus simpler models
based on momentum theory or potential flow. However, CFD can be computationally
expensive when done in three dimensions, but may be necessary to predict
performance for low aspect ratio or variable radius rotors, and to predict the
unique flow field produced by CFTs, and therefore wake recovery and interaction,
which is discussed in detail later.
